\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-11-12 paper.tex
improved table layout

\begin{table*}[b]
  \centering
  \bgroup
  \def\arraystretch{1.3}
  \begin{tabular}{llrrrrrrr}
\toprule
              &            & base  & \multicolumn{2}{c}{watchdog} & \multicolumn{2}{c}{reputation} & \multicolumn{2}{c}{both} \\
\midrule
size (bytes)  & manual     & 10466 & 15530 &  +48\% & 13306 &  +27\% & 18334 &  +75\%\\
              & generated  & 10466 & 18352 &  +75\% & 16376 &  +56\% & 20998 & +101\%\\
\cline{2-9}
              & difference &     0 &  2822 &  +18\% &  3070 &  +23\% &  2664 &  +15\%\\
\hline
packets sent  & manual     &    20 &    51 & +155\% &    32 &  +60\% &    63 & +215\%\\
              & generated  &    20 &    49 & +145\% &    32 &  +60\% &    55 & +175\%\\
\cline{2-9}
              & difference &     0 &    -2 &   -4\% &     0 &   0\% &    -8 &   -13\%\\
\hline
bytes sent    & manual     &   476 &  1933 & +306\% &   860 &  +81\% &  2317 & +387\%\\
              & generated  &   476 &  1897 & +299\% &   884 &  +86\% &  2161 & +354\%\\
\cline{2-9}
              & difference &     0 &   -36 &   -2\% &    24 &   +3\% &  -156 &   -7\%\\
\hline
execution
time ($\mu$s) & manual     &    48 &    94 &  +96\% &    88 &  +83\% &   149 & +210\%\\
              & generated  &    48 &   121 & +152\% &   121 & +152\% &   138 & +188\%\\
\cline{2-9}
              & difference &     0 &    27 &  +29\% &    33 &  +38\% &   -11 &   -7\%\\
\bottomrule
  \end{tabular}
  \egroup
  \caption{Results and Side-by-Side Comparison.}
  \label{tbl:results}
\end{table*}

>>>>

% table goes here, because a spanning table is placed on the next page, relative
% to where it's defined.
\begin{table*}[b]
  \centering
  \begin{tabular}{llrrrrrrr}
\toprule
              &            & base  & \multicolumn{2}{c}{watchdog} & \multicolumn{2}{c}{reputation} & \multicolumn{2}{c}{both} \\
\midrule
image
size (bytes)  & manual     & 10466 & 15530 &  +48\% & 13306 &  +27\% & 18334 &  +75\%\\
              & generated  & 10466 & 18352 &  +75\% & 16376 &  +56\% & 20998 & +101\%\\
\cmidrule{2-9}
              & difference &     0 &  2822 &  +18\% &  3070 &  +23\% &  2664 &  +15\%\\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{total packets sent\\in a window of 90s}}
              & manual     &    20 &    51 & +155\% &    32 &  +60\% &    63 & +215\%\\
              & generated  &    20 &    49 & +145\% &    32 &  +60\% &    55 & +175\%\\
\cmidrule{2-9}
              & difference &     0 &    -2 &   -4\% &     0 &   0\% &    -8 &   -13\%\\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{total bytes sent\\in a window of 90s}}
              & manual     &   476 &  1933 & +306\% &   860 &  +81\% &  2317 & +387\%\\
              & generated  &   476 &  1897 & +299\% &   884 &  +86\% &  2161 & +354\%\\
\cmidrule{2-9}
              & difference &     0 &   -36 &   -2\% &    24 &   +3\% &  -156 &   -7\%\\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{event loop\\average duration ($\mu$s)}}
              & manual     &    48 &    94 &  +96\% &    88 &  +83\% &   149 & +210\%\\
              & generated  &    48 &   121 & +152\% &   121 & +152\% &   138 & +188\%\\
\cmidrule{2-9}
              & difference &     0 &    27 &  +29\% &    33 &  +38\% &   -11 &   -7\%\\
\bottomrule
  \end{tabular}
  \caption{Results and Side-by-Side Comparison.}
  \label{tbl:results}
\end{table*}
